RILS-ROLS: Robust Symbolic Regression via Iterated Local Search and Ordinary Least Squares

### 2022-09-14 doc/paper.tex
working...

\setcounter{tocdepth}{3}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{comment}
\usepackage{placeins}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
 \usepackage{booktabs}
\usepackage{array}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{booktabs}
\usepackage{bookmark}% faster updated bookmarks
\usepackage{hypcap} % fix the links
\evensidemargin\oddsidemargin
\usepackage{graphicx}
\pagestyle{plain}
\usepackage{xcolor}
\newcommand\ToDo[1]{\textcolor{red}{#1}}

\usepackage{xspace}
\usepackage{color}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{changes}

@@

	 Machine learning--based methods to solve SR are based on Bayesian symbolic regression (BSR)~\cite{jin2019bayesian} which belongs to the family of Markov Chain Monte Carlo algorithms. Deep Symbolic Regression (DSR), a RNN approach, is proposed in~\cite{petersen2019deep} utilizing the policy gradient search. This mechanism of search is further considered in~\cite{landajuela2021improving}. A fast neural network approach, called OccamNet,  is proposed in~\cite{costa2020fast}.  A deep reinforcement learning approach enhanced with genetic programming is given in~\cite{mundhenk2021symbolic}.

@@

	 \begin{table}[!ht]
		\centering
		\begin{tabular}{l l l} \\ \hline
			Algorithm          &   paper/year &   Short details   \\ \hline
			Eurequa                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
			APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection                \\ 
		     \fxnote{TODO}  &      & 
		\end{tabular}
		\caption{Overview of SR methods.}
		\label{tab:gp-based}
	\end{table}

>>>>

\setcounter{tocdepth}{3}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{comment}
\usepackage{placeins}
\usepackage{mathtools}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage[utf8]{inputenc}
 \usepackage{booktabs}
\usepackage{array}
\usepackage[pdfencoding=auto,psdextra]{hyperref}
\usepackage{booktabs}
\usepackage{bookmark}% faster updated bookmarks
\usepackage{hypcap} % fix the links
\evensidemargin\oddsidemargin
\usepackage{graphicx}
\pagestyle{plain}
\usepackage{xcolor}
\newcommand\ToDo[1]{\textcolor{red}{#1}}
 \usepackage{tabularx}
\usepackage{xspace}
\usepackage{color}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{amsthm}
%\usepackage{changes}

@@

	 Machine learning--based method   based on Bayesian symbolic regression (BSR) is proposed in~\cite{jin2019bayesian},  belongs to the family of Markov Chain Monte Carlo algorithms. Deep Symbolic Regression (DSR), a RNN approach, is proposed in~\cite{petersen2019deep} utilizing the policy gradient search. This mechanism of search is further investigated in~\cite{landajuela2021improving}. A fast neural network approach, called OccamNet,  is proposed in~\cite{costa2020fast}.  A deep reinforcement learning approach enhanced with genetic programming is given in~\cite{mundhenk2021symbolic}.

@@

	 \begin{table}[htb]
		\centering
		\begin{tabularx}{350pt}{l  l  X}  
			Algorithm          &   paper/year &   Short details   \\ \hline
	        Hybrid GP  &   \cite{raidl1998hybrid} (1998)   & GP--based method; solutions locally optimizes by method of least squares to find optimum coefficients for top-level terms \\ 
	        DFE        & \cite{cerny2008using} (2008)   & Differential evolution algorithm \\
			Eurequa                & \cite{schmidt2009distilling, schmidt2011machine} (2009, 2011) & Age-fitness pareto optimization approach using co-evolved fitness estimation   \\
			APF            &      \cite{schmidt2010age} (2010)        &  Age-fitness pareto optimization approach                        \\
			EPLEX          &      \cite{la2016epsilon} (2016)         &   A parent selection method called $\epsilon$--lexicase selection                \\ 
	       Local optimization     & \cite{kommenda2018local}   & Constants Optimization in GP by Nonlinear Least Square \\
	       \fxnote{TODO}             &      & 
		\end{tabularx}
		\caption{Overview of methods to solve SR.}
		\label{tab:gp-based}
	\end{table}
